Supporting Information for "Geometric models overestimate lake depth due to imperfect slope measurement"

### 2020-07-16 manuscript/si_template_2019.tex
fix supp fig listing

\item \textbf{Figure S2:} Comparison between reported depth and depth extracted from bathymetry surfaces

\item \textbf{Figure S3:} Comparison of lake characteristics according to differences in lake cross-section shape or reservoir status

\item \textbf{Figure S4:} Hypsography classification by state

\item \textbf{Figure S5:} Comparison among lake shape and reservoir classes for true and proxy geometry measures

\item \textbf{Figure S6:} Importance plot for random forest variables showing increase in mean square error

@@

\clearpage
\begin{figure}
      \noindent\includegraphics[width=0.85\textwidth]{../figures/01_contrasts-1}
      \caption{Comparison of lake characteristics according to differences in lake cross-section shape or reservoir status.}\label{figs3}
      \end{figure}

@@

\begin{figure}
      \noindent\includegraphics[width=0.85\textwidth]{../figures/lgnemanual-vs-bathy-depth-1}
      \caption{Comparison between reported depth and depth extracted from bathymetry surfaces by US State where reported depths come from the LAGOSUS-Depth product \cite{stachelek2020}. For this figure, no reported depth values originated from the same source as its corresponding bathymetry-derived value.}\label{figs2}
      \end{figure}

>>>>

\item \textbf{Figure S2:} Hypsography classification by state

\item \textbf{Figure S3:} Comparison among lake shape and reservoir classes for true and proxy geometry measures

\item \textbf{Figure S4:} Importance plot for random forest variables showing increase in mean square error

\item \textbf{Figure S5:} Comparison between characteristics of lakes with bathymetry data against lakes with depth from other sources

\item \textbf{Figure S6:} Comparison of lake characteristics according to differences in lake cross-section shape or reservoir status

\item \textbf{Figure S7:} Comparison between reported depth and depth extracted from bathymetry surfaces

@@

\clearpage
\begin{figure}
      \begin{center}\includegraphics[width=0.85\textwidth]{../figures/01_contrasts-1}\end{center}
      \caption{Comparison of lake characteristics according to differences in lake cross-section shape or reservoir status.}\label{figs3}
      \end{figure}

@@

\begin{figure}
      \begin{center}\includegraphics[width=0.73\textwidth]{../figures/lgnemanual-vs-bathy-depth-1}\end{center}
      \caption{Comparison between reported depth and depth extracted from bathymetry surfaces by US State where reported depths come from the LAGOSUS-Depth product \cite{stachelek2020}. For this figure, no reported depth values originated from the same source as its corresponding bathymetry-derived value.}\label{figs2}
      \end{figure}
